A publishing infrastructure for AI-assisted academic authoring

### 2023-07-11 latex/manuscript.tex
add an structured abstract

In this work, we investigate how models with advanced natural language processing capabilities can be used to reduce the time-consuming process of writing and revising scholarly manuscripts.
To this end, we integrate large language models into the Manubot publishing ecosystem to suggest revisions for scholarly text.
Our AI-based revision workflow uses a prompt generator that integrates metadata from the manuscript into prompt templates to generate section-specific instructions for the language model.
Then, the model generates a revised version of each paragraph that the human author can review.
We tested our AI-based revision workflow in three case studies of existing manuscripts, including the present one.
Our results suggest that these models can capture the concepts in the scholarly text and produce high-quality revisions that improve clarity.
All changes to the manuscript are tracked using a version control system, providing transparency into the human or machine origin of text.
Given the amount of time that researchers put into crafting prose, we anticipate that this advance will significantly improve the type of knowledge work performed by academics.

>>>>

\textbf{Objective:} Investigate how models with advanced natural language processing capabilities can reduce the time-consuming process of writing and revising scholarly manuscripts.\\
\textbf{Materials and Methods:} To this end, we integrate large language models into the Manubot publishing ecosystem to suggest revisions for scholarly text.
Our AI-based revision workflow uses a prompt generator that integrates metadata from the manuscript into prompt templates to generate section-specific instructions for the language model.
Then, the model generates a revised version of each paragraph that the human author can review.
We tested our AI-based revision workflow in three case studies of existing manuscripts, including the present one.\\
\textbf{Results:} Our results suggest that these models can capture the concepts in the scholarly text and produce high-quality revisions that improve clarity.
All changes to the manuscript are tracked using a version control system, providing transparency into the human or machine origin of text.\\
\textbf{Conclusions:} Given the amount of time that researchers put into crafting prose, incorporating large language models into the scholarly writing process can significantly improve the type of knowledge work performed by academics.
It can also help scholars to focus on the most important aspects of their work, such as the novelty of their ideas, and automate the most tedious parts such as adhering to a certain writing style.
Although the use of AI-assisted tools for scientific authoring is controversial, our work focuses on revising text written by humans and provides transparency into the origin of text by tracking changes, which can alleviate concerns about the use of AI in scientific authoring.
